### 2023-05-15 application.tex
sections

\section{Solving resilience}

\noindent
\subsection{Computing the maximal resilient subsystem}

@@

\alain{probablement enlever toute la suite et garder seulement un point sur les VASS}

In this section, we study the general resilience problem.

@@

Since for  lossy channel systems $\pred^*(L)$ with $L=\uparrow L$ is a computable (upward-closed) regular language, we deduce :

@@

\begin{proof}
\alain{faire d'abord la preuve pour les VASS.}
\end{proof}

@@

\begin{proof}
		Recall that reachability is NP-complete for integer VASS. We consider semilinear sets in $\mathbb{Z}^d$.
\end{proof}

@@

\begin{proof}
The reachability relation of continuous VASS is definable by a sentence of linear size in the existential theory of
the rationals with addition and order whose complexity is EXPSPACE. Hence, $\Bad \subseteq \pred^*(\Safe)$ is also decidable in EXPSPACE. \alain{and may be in coNP-complete. Recall that reachability is P-complete for continuous VASS}
\end{proof}

@@

\begin{proof}
Consider a given $k \in \N$.
Consider $\Bad \subseteq \N^d$ upward-closed and $\Safe \subseteq \N^d$ downward-closed.
Consider a given vector addition system $V$, which has a finite number of transitions.
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition of $V$.

@@

\begin{proposition}
{\sc $k$-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable.
\end{proposition}

\begin{proof}
Consider a given $k \in \N$.
Consider $\Bad \subseteq Q \times \N^d$ upward-closed and 
% $\Safe \subseteq Q \times \N^d$
$\Safe = S \setminus \Bad$
 downward-closed.
Consider a given VASS $V$, which has a finite number of transitions.
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition.

@@

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable.
\end{proposition}

>>>>

\section{Computing the maximal resilient subsystem}

@@

\section{Deciding resilience for extended automata}

@@

Since for lossy channel systems $(Q, \Sigma,d,...)$ with $d$ fifo channels and a set $L \subseteq Q \times (\Sigma^*)^d$, the set $\pred^*(\uparrow L)$ is a computable upward-closed regular language, we deduce :

@@

\begin{proof}
\alain{faire la preuve pour les VASS.}
\end{proof}

@@

\begin{proof}
	\alain{à faire}	Recall that reachability is NP-complete for integer VASS. We consider semilinear sets in $\mathbb{Z}^d$.
\end{proof}

@@

\begin{proof}
The reachability relation of continuous VASS is definable by a sentence of linear size in the existential theory of
the rationals with addition and order whose complexity is EXPSPACE. Hence, $\Bad \subseteq \pred^*(\Safe)$ is also decidable in EXPSPACE \cite{ref}. 
%			\alain{and may be in coNP-complete. Recall that reachability is P-complete for continuous VASS}
\end{proof}

@@

\begin{proof}
Consider a given $k \in \N$.
Consider $\Bad \subseteq \N^d$ upward-closed and $\Safe \subseteq \N^d$ downward-closed.
Consider a given vector addition system $V$, \alain{bizarre de dire ça "which has a finite number of transitions."}
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition of $V$.

@@

\begin{proposition}
{\sc $k$-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable.
\end{proposition}\alain{quelle complexité ?}

\begin{proof}
Let a given $d$-VASS $V$ and consider a given $k \in \N$.
Consider $\Bad \subseteq Q \times \N^d$ upward-closed and 
% $\Safe \subseteq Q \times \N^d$
$\Safe = S \setminus \Bad$
 downward-closed.
Let us call $c_{\max}$ the maximal absolute value of a constant appearing in a coordinate of a transition.

@@

\begin{proposition}
{\sc Bounded-resilience } in VASS when $\Bad = \uparrow \Bad$ and $\Safe = S \setminus \Bad$ is decidable. \alain{quelle complexité ?}
\end{proposition}
